---
title: "Example 2"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Options to Code Chunks

Code chunks can be passed options:

```{r, echo = FALSE}
data(iris)
plot(Petal.Width ~ Petal.Length, data = iris)
```

```{r, echo = FALSE, fig.width = 5, fig.height = 3}
plot(Petal.Width ~ Petal.Length, data = iris)
```


### Inline Code

We can also include R code inline. For example, the mean of Petal.Length is `r round(mean(iris$Petal.Length), 2)`. 

## Nice Output 

There are various auxiliary packages that can produce nice output as well.

```{r}
head(iris)
```

```{r}
library(kableExtra)
kable(head(iris), format = "markdown", align = c('ccccl'))
```

```{r}
m <- lm(Petal.Width ~ ., data = iris)
summary(m)
df <- data.frame(summary(m)$coef)
names(df) <- c("Estimate", "Std. Error", "t", "p-value")
kable(df,
      format = "markdown",
      digits = 2,
      align = "c") %>% 
  kable_styling(bootstrap_options = "striped", full_width = F)
```

## Equations

The model's \(R^2\) value is `r round(summary(m)$r.squared, 3)`. The model we fit was:

\begin{align*}
  E(\textrm{Petal.Width} | X) = \beta_0 &+ \beta_1\textrm{Petal.Length} \\
  &+ \beta_2\textrm{Sepal.Width} \\
  &+ \beta_3\textrm{Sepal.Length} \\
  &+ \beta_4I_{\textrm{Species = "versicolor"}} \\
  &+ \beta_5I_{\textrm{Species = "virginica"}}.
\end{align*}

The gaussian PDF is

\[
  f(x | \mu, \sigma^2) = \frac{1}{\sqrt{2\pi\sigma^2}}e^{-\frac{(x - \mu)^2}{2\sigma^2}}.
\]